---
title: "Assignment#1 R Basic"
author: "Boyie Chen 陳柏瑜"
date: "2020-09-25"
output:
  html_document:
    highlight: zenburn
    number_sections: yes
    theme: cerulean
    toc: yes
    #css: style.css
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Practice_01_2_1: Filtering data
```{r}
x.a <- rnorm(1000, 1, 10)

# 1.1 Filter OUT extreme values out of two standard deviations
sd <-sd(x.a)
x.a <- x.a[x.a>-2*sd & x.a<2*sd]
# 1.2 Plotting the distribution of the remaining vector x.a
hist(x.a)

# 1.3 Calculate the 25% 50% and 75% quantile of vector x.a. (You may google "quantile r)
x.a_quantile <- quantile(x.a, c(0.25, 0.5, 0.75))
x.a_quantile
# 1.4 Get the sequence between 25% to 75% of x.a
#seq(from = quantile(x.a, 0.25), to  = quantile(x.a, 0.75))
sort(x.a[x.a>=x.a_quantile[1] & x.a<=x.a_quantile[3]])

```



# Practice01_2_2: Accessing characters
```{r}
x.b <- c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j", "k")

# 2.1 Get only elements at odd positions
x.b[seq(1,length(x.b),2)]
# 2.2 Truncate the first 2 elements and the last 2 elements
x.b[3:(length(x.b)-2)]
```


# Practice01_2_3: Sorting
```{r}
population <- c(158228, 126687, 228075, 204903, 308383)
town <- c("中正", "大同", "中山", "松山", "大安")

# 3.1 Sort the population, 
# the reuslt should be [1] 126687 158228 204903 228075 308383
sort(population)

# 3.2 Sort populations in decreasing order 
# (Google it or check help)
# Result: [1] 308383 228075 204903 158228 126687
sort(population, decreasing = T)
# 3.3 Sort town names according to population in decreasing order
# Result: [1] "大安" "中山" "松山" "中正" "大同"
names(population) <- town
names(sort(population, decreasing = T))
```


# PracticeR01_2_4: Using google to solve following questions
```{r}
# 4.1 Print current time
# e.g., "2019-09-02 21:31:36 CST"
systime <- Sys.time()
systime
# 4.2 Check the data type of current time
class(systime)

# 4.3 Print today
# e.g., [1] "2019-09-02"
sysdate <- Sys.Date()
sysdate

# 4.4 Check the data type of date
class(sysdate)

# 4.5 Write example to compare following functions: print(), cat(), and message() 
print(sysdate)
cat(sysdate)
message(sysdate)
```


# PracticeR01_2_5: Using google: measure running time
```{r}
# 5.1 Using google to find out how to measure the runing time of the following code
start_time <- Sys.time()
x <- rnorm(10000000, 1, 10) 
plot(density(x))
end_time <- Sys.time()
runtime <- end_time-start_time
print(runtime)
```


# Practice_01_3_1

* 底下有個data.frame有兩個variable，`order(df2$a, df2$b)`是先照`a`還是`b`排序呢？那如果加上負號又是什麼意思呢？


```{r}
a <- c(5, 5, 5, 5, 4, 4, 4, 3, 3, 1, 1, 1, 2, 2, 2)
b <- c(3, 3, 3, 4, 4, 4, 2, 2, 2, 4, 4, 1, 4, 1, 1)
df2 <- data.frame(a, b)

df2[order(df2$a, df2$b),]
# sort df2 in orders of decreasing b then increasing a
df2 <- df2[order(df2$a, -df2$b),]

```

`df2[order(df2$a, df2$b),]`是先按照`a`由小到大排序，在同樣的`a`值內再按照`b`由小到大排序。
`df2[order(df2$a, -df2$b),]` 加上負號則是在排序`b`時由大到小排序。

# Practice_01_3_2

* 先將以下三個vectors合併為一個data.frame，並先就出口再入口的比例，由大而小排列後，覆蓋掉原本的data.frame。
```{r}
country <- c("CN", "US", "JP", "HK", "KR", "SG", "DE", "MY", "VN", "PH", "TH", "AU", "NL", "SA", "ID", "GB", "IN", "FR", "IT", "AE")

import <- c(26.142, 12.008, 7.032, 13.646, 4.589, 5.768, 2.131, 2.802, 3.428, 3.019, 1.976, 1.118, 1.624, 0.449, 0.983, 1.302, 1.027, 0.553, 0.670, 0.455)

export <- c(22.987, 12.204, 11.837, 7.739, 5.381, 4.610, 2.866, 2.784, 2.414, 2.092, 1.839, 1.788, 1.665, 1.409, 1.391, 1.075, 0.974, 0.899, 0.800, 0.728)

df <- data.frame(country, export, import)
df <- df[order(-export, -import),]
df
```




